The \dealii Library, Version 9.0

### 2018-05-09 9.0/paper.tex
Edit the part on manifolds.
We have not yet removed Boundary or things like
Triangulation::get_boundary, but they are now deprecated (as of last
August).

\dealii{} has had the ability to attach \textit{manifold descriptions}
to all parts of a geometry for several releases already. These
descriptions are used when considering where to place new vertices
upon mesh refinement, in determining the mapping from reference cell
to real cell, and in a number of other contexts. However, for historical
reasons, manifold descripts have used some of the same code paths also
used for boundary indicators typically used to identify which parts of
the boundary correspond to what boundary conditions.

This connection has been severed in the current release: Boundary
indicators and manifold descriptions are now entirely separated. Furthermore,
all functions that allowed to query for old-style \texttt{Boundary} objects (deprecated
since version 8.5 of the \dealii library) have been removed, and have been
replaced by the equivalent methods that query \texttt{Manifold} classes.

>>>>

\dealii{} has had the ability to attach \textit{manifold descriptions} to all
parts of a geometry since the 8.2 release. These descriptions are used to place
new vertices during mesh refinement, to determine the mapping between the
reference and real cells, and in a number of other contexts. These classes,
inheriting from \texttt{Manifold}, describe coordinate transformations in a
general way and completely supersede the older classes inheriting from
\texttt{Boundary}. However, for historical reasons, manifold descriptors have
used some of the same code paths as boundary indicators, which were only
intended for marking what parts of the boundary correspond to what boundary
conditions. Put another way: under certain circumstances a boundary indicator
was also interpreted as a manifold indicator.

The current release severs this connection: Boundary indicators and manifold
descriptions are now entirely separated. This means that \texttt{boundary\_id}s
are only used to set boundary conditions and \texttt{manifold\_id}s are only
used to set geometry descriptions. The old compatibility code for using boundary
indicators as manifold indicators has been removed and all usages of the
old-style \texttt{Boundary} objects (even with manifold ids) are now deprecated.
